---
title: "Project Proposal"
author: "JRLK - Jess Ringness, Rebekah Kim, Laura Cai, Karen Dong"
format: pdf
execute: 
  warning: false
  message: false
editor: visual
---

```{r}
#| label: load-pkg-data
library(tidyverse)
library(tidymodels)
job_postings <-read.csv("data/job_postings.csv")
benefits <-read.csv("data/benefits.csv")
employee <-read.csv("data/employee_counts.csv")
```

```{r manipulating_benefits}
benefits <- benefits |>
  select(-inferred) |>
  mutate(count = 1) |>
  pivot_wider(names_from = "type", values_from = "count")
```


```{r joining_jobs_employee}
jobs_employee <- job_postings |>
  left_join(employee, by = join_by("company_id"))
```

```{r joining_final_set}
linkedin <- jobs_employee |>
  left_join(benefits, by = join_by("job_id"))
```

## Introduction

...

## Data description

...

## Initial exploratory data analysis

```{r drop_na_1}
linkedin <- linkedin |> 
  drop_na(applies)
```

```{r plot_hist_applications}
linkedin |>
  ggplot(aes(x = applies)) +
  geom_histogram(binwidth = 20) +
  labs(x = "Number of Applications Recieved",
       y = "Count of Job Listings",
       title = "Distribution of the Number of Applications Recieved") 
```

```{r}
summary(linkedin$applies)
```

The distribution of the number of applications for a job listing on LinkedIn is right-skewed and uni-modal, with fewer applications for a job listing most prevalent. Given that the distribution is skewed, the center is 4.00 applications, as estimated by the median. The IQR describing the spread of the middle 50% of data is 12 applications (13 - 1). 

There are a couple of outliers with a high number of applications. 

```{r}
job_postings |>
  ggplot(aes(x = applies, y = views, color = pay_period)) +
  geom_point() + 
  facet_wrap(~pay_period)
```

```{r}
job_postings |>
  ggplot(aes(x = applies, y = views, color = pay_period)) +
  geom_point() 
```

```{r}
job_postings |>
  ggplot(aes(x = applies, y = views, color = formatted_work_type)) +
  geom_point() + 
  facet_wrap(~formatted_work_type)
```

```{r}
job_postings_exp_na <- job_postings |> 
  drop_na(formatted_experience_level) |>
  filter(formatted_experience_level != "")
```

```{r}
job_postings_exp_na |>
  ggplot(aes(x = applies, y = views, color = formatted_experience_level)) +
  geom_point() + 
  facet_wrap(~formatted_experience_level)
```

```{r}
job_postings |>
  ggplot(aes(x = max_salary, y = views)) +
  geom_point()
```

```{r}
job_postings |>
  ggplot(aes(x = applies, y = views)) +
  geom_point()
```

```{r}
job_postings |>
  ggplot(aes(x = max_salary, y = views, color = sponsored)) +
  geom_point() + 
  facet_wrap(~sponsored)
```

```{r}
unique(job_postings$sponsored)
```

## Analysis approach

...

## Data dictionary

The data dictionary can be found [here](ADD%20LINK!!!) \[Update the link and remove this note!\]
