---
title: "Your project title"
author: "Team Name: Team member 1, Team member 2, Team member 3, Team member 4"
date: "Update date"
format: pdf
execute: 
  warning: false
  message: false
  echo: false
editor: visual
---

```{r}
#| label: load packages and data

```

Your written report goes here!

::: callout-important
Before you submit, make sure your code chunks are turned off with `echo: false` and there are no warnings or messages with `warning: false` and `message: false` in the YAML.
:::

￼


```{r}
#| label: load packages and data
library(tidyverse)
library(tidymodels)
library(knitr)
library(patchwork)
job_postings <-read.csv("data/job_postings.csv")
benefits <-read.csv("data/benefits.csv")
employee <-read.csv("data/employee_counts.csv")
```

Your written report goes here!

::: callout-important
Before you submit, make sure your code chunks are turned off with `echo: false` and there are no warnings or messages with `warning: false` and `message: false` in the YAML.
:::


```{r manipulating_benefits}
#| echo: false
benefits <- benefits |>
  select(-inferred) |>
  mutate(count = 1) |>
  pivot_wider(names_from = "type", values_from = "count")
```

```{r}

benefits <- replace(benefits, is.na(benefits), 0)
benefits$tot_benefits <- rowSums(benefits == 1)
benefits_total <- benefits[, c('job_id', 'tot_benefits')]
```



```{r joining_jobs_employee}
#| echo: false
jobs_employee <- job_postings |>
  left_join(employee, by = join_by("company_id"))
```

```{r joining_final_set}
#| echo: false
linkedin <- jobs_employee |>
  left_join(benefits_total, by = join_by("job_id"))

linkedin_yearly <- linkedin |> 
  distinct(job_id, .keep_all = TRUE) |>
  mutate(per_applies = applies/views) |>
  filter(per_applies < 1) |>
  filter(pay_period == "YEARLY") |>
  mutate(original_listed_time = as.POSIXct(original_listed_time/1000, origin = "1970-01-01", tz = "EST")) 

linkedin_yearly$hour <- sapply(strsplit(as.character(linkedin_yearly$original_listed_time), ' '), function(x) {
  time_parts <- unlist(strsplit(x[2], ':'))
  return(time_parts[1])
})
```

```{r}
linkedin_yearly
```

```{r}
linkedin_yearly |>
  ggplot(aes(x = hour, y = per_applies)) + 
  geom_point()
```



```{r}
# Sample data frame
data <- data.frame(timestamp = c('2023-11-12 08:30:45', '2023-11-12 15:45:20', '2023-11-12 22:10:05'))

# Splitting timestamp and extracting the hour
data$hour <- sapply(strsplit(as.character(data$timestamp), ' '), function(x) {
  time_parts <- unlist(strsplit(x[2], ':'))
  return(time_parts[1])
})

# Display the resulting data frame
print(data)

```


```{r}
linkedin_yearly
```

```{r}
#1692732000000
timestamp <- 1692732000

#timestamp <- 1692817626
formatted_date <- as.POSIXct(timestamp, origin = "1970-01-01", tz = "UTC")
print(formatted_date)

```



```{r}
linkedin_yearly |>
  filter(employee_count < 1000) |>
  ggplot(aes(x = employee_count, y = per_applies)) + 
  geom_point()
```


```{r}
linkedin_hourly <- linkedin |> 
  distinct(job_id, .keep_all = TRUE) |>
  mutate(per_applies = applies/views) |>
  filter(per_applies < 1) |>
  filter(pay_period == "YEARLY")
```


```{r}
set.seed(210)
linkedin_split <- initial_split(linkedin_yearly, prop = 0.8)
linkedin_train <- training(linkedin_split)
linkedin_test <- testing(linkedin_split)
```

```{r}
linkedin_train
```


```{r}

linkedin_yr_rec <- recipe(per_applies ~ job_id + max_salary + follower_count + formatted_experience_level, data = linkedin_train) |> 
  update_role(job_id, new_role = "ID") |> 
  step_mutate(max_salary = max_salary / 1000000) |>
  step_mutate(follower_count = follower_count / 100000000) |>
  step_naomit(all_predictors()) |>
  step_dummy(all_nominal_predictors()) |> 
  step_zv(all_predictors())
```

```{r}
linkedin_yr_rec1 <- recipe(per_applies ~ job_id + max_salary + follower_count, data = linkedin_train) |> 
  update_role(job_id, new_role = "ID") |> 
  step_mutate(max_salary = max_salary / 1000000) |>
  step_mutate(follower_count = follower_count / 100000000) |>
  step_naomit(all_predictors()) |>
  step_dummy(all_nominal_predictors()) |> 
  step_zv(all_predictors())
```

```{r}

linkedin_yr_rec_ben <- recipe(per_applies ~ job_id + max_salary + tot_benefits, data = linkedin_train) |> 
  update_role(job_id, new_role = "ID") |> 
  step_mutate(max_salary = max_salary / 1000000) |>
  #step_mutate(follower_count = follower_count / 100000000) |>
  step_naomit(all_predictors()) |>
  step_dummy(all_nominal_predictors()) |> 
  step_zv(all_predictors())
```

```{r}
linkedin_yr_rec_hr <- recipe(per_applies ~ job_id + max_salary + hour, data = linkedin_train) |> 
  update_role(job_id, new_role = "ID") |> 
  step_mutate(max_salary = max_salary / 1000000) |>
  step_naomit(all_predictors()) |>
  step_dummy(all_nominal_predictors()) |> 
  step_zv(all_predictors())
```




```{r}
#specify the model
linkedin_yr_spec <- linear_reg() |>
  set_engine("lm")

#build model workflow
linkedin_yr_workflow <- workflow() |>
  add_model(linkedin_yr_spec) |>
  add_recipe(linkedin_yr_rec) 

# fit the model 
linkedin_yr_fit <- linkedin_yr_workflow |>
  fit(data = linkedin_train) 

tidy(linkedin_yr_fit) |>
  kable(digits = 3)
```

```{r}
#specify the model
linkedin_yr_spec1 <- linear_reg() |>
  set_engine("lm")

#build model workflow
linkedin_yr_workflow1 <- workflow() |>
  add_model(linkedin_yr_spec1) |>
  add_recipe(linkedin_yr_rec1) 

# fit the model 
linkedin_yr_fit1 <- linkedin_yr_workflow1 |>
  fit(data = linkedin_train) 

tidy(linkedin_yr_fit1) |>
  kable(digits = 3)
```

```{r}
#specify the model
linkedin_yr_spec_ben <- linear_reg() |>
  set_engine("lm")

#build model workflow
linkedin_yr_workflow_ben <- workflow() |>
  add_model(linkedin_yr_spec_ben) |>
  add_recipe(linkedin_yr_rec_ben) 

# fit the model 
linkedin_yr_fit_ben <- linkedin_yr_workflow_ben |>
  fit(data = linkedin_train) 

tidy(linkedin_yr_fit_ben) |>
  kable(digits = 3)
```
```{r}
#specify the model
linkedin_yr_spec_hr <- linear_reg() |>
  set_engine("lm")

#build model workflow
linkedin_yr_workflow_hr <- workflow() |>
  add_model(linkedin_yr_spec_hr) |>
  add_recipe(linkedin_yr_rec_hr) 

# fit the model 
linkedin_yr_fit_hr <- linkedin_yr_workflow_hr |>
  fit(data = linkedin_train) 

tidy(linkedin_yr_fit_hr) |>
  kable(digits = 3)
```


BIC-- -2771, -2757, -1315
```{r}
glance(linkedin_yr_fit1)
```

```{r}
glance(linkedin_yr_fit)
```
```{r}
glance(linkedin_yr_fit_ben)
```

```{r}
glance(linkedin_yr_fit_hr)
```

```{r}
linkedin_yr_fit_5 <- linear_reg() |>
  fit(per_applies~ hour + max_salary, data = linkedin_train) 

glance(linkedin_yr_fit_5)
```

```{r}
linkedin_yr_fit_5 <- linear_reg() |>
  fit(per_applies~ sponsored, data = linkedin_train) 

glance(linkedin_yr_fit_5)
```


```{r}
linkedin_new <- linkedin_yearly |>
  mutate(applied_10 = if_else(per_applies > 0.1, 1, 0))
```


```{r}
linkedin_new <- linkedin_yearly |>
  mutate(applied_10 = if_else(per_applies > 0.1, 1, 0))
linkedin_new$applied_10 <- as.factor(linkedin_new$applied_10)
linkedin_new
```

```{r}
linkedin_new <- linkedin_yearly |>
  mutate(applied_10 = if_else(per_applies > 0.1, 1, 0))
linkedin_new$applied_10 <- as.factor(linkedin_new$applied_10)

set.seed(210)

linkedin_split_new <- initial_split(linkedin_new)
linkedin_train_new <- training(linkedin_split_new)
linkedin_test_new  <- testing(linkedin_split_new)


linkedin_yr_fit_log <- logistic_reg() |>
  set_engine("glm") |>
  fit(applied_10~ max_salary, data = linkedin_train_new, family = "binomial") 

glance(linkedin_yr_fit_log)
```

```{r}
linkedin_pred <- predict(linkedin_yr_fit_log, linkedin_test_new, type = "prob") |> 
  bind_cols(linkedin_test_new) 

linkedin_pred |>
  roc_curve(
    truth = applied_10,
    .pred_1,
    event_level = "second"
  ) |>
  autoplot()
```



```{r}
linkedin_new
```


```{r}
linkedin_new |>
  ggplot(aes(x = tot_benefits, y = per_applies)) + 
  geom_point()
```

```{r}
linkedin_new
```



__

```{r}
linkedin_yearly |>
  ggplot(aes(x = views)) + 
  geom_histogram() + 
  geom_vline(xintercept = 200)
```



```{r}
linkedin_yr_rec <- recipe(per_applies ~ job_id + max_salary + follower_count + formatted_experience_level, data = linkedin_train) |> 
  update_role(job_id, new_role = "ID") |> 
  step_mutate(max_salary = max_salary / 1000000) |>
  step_mutate(follower_count = follower_count / 100000000) |>
  step_naomit(all_predictors()) |>
  step_dummy(all_nominal_predictors()) |> 
  step_zv(all_predictors())
```


```{r}
#specify the model
linkedin_yr_spec <- linear_reg() |>
  set_engine("lm")

#build model workflow
linkedin_yr_workflow <- workflow() |>
  add_model(linkedin_yr_spec) |>
  add_recipe(linkedin_yr_rec) 

# fit the model 
linkedin_yr_fit <- linkedin_yr_workflow |>
  fit(data = linkedin_train) 

tidy(linkedin_yr_fit) |>
  kable(digits = 3)
```

```{r}
glance(linkedin_yr_fit)
```







The `linkedin` dataset must drop_na values for relevent variables, and the `pay_period` dataset must be recoded such that it is a numerical variable of the number of pay periods in a year. The `annual_max_salary` can then be calculated by multiplying the number of periods by the maximum pay. The `benefits` data was also manipulated so that each is a dummy variable. In the final analysis, more manipulations will be done as needed.

```{r drop_na}
#| echo: false
linkedin <- linkedin |> 
  drop_na(applies)

linkedin <- linkedin |> 
  drop_na(pay_period) 
  
linkedin <- linkedin |>
  drop_na(max_salary) 

linkedin <- linkedin |>
  drop_na(views) 

linkedin <- linkedin |>
  drop_na(follower_count) 
```

```{r mutate_pay_nums}
#| warning: false
#| echo: false
linkedin <- linkedin |>
  mutate(pay_period = recode(pay_period, YEARLY = 1, HOURLY = 2080))
```

```{r annual_salary_manipulation}
#| echo: false
linkedin <- linkedin |>
   mutate(annual_max_salary = pay_period * max_salary/1000)
```

```{r plot_hist_applications}
#| echo: false
#| fig_width: 5 
#| fig_height: 1.5
views_dist <- linkedin |>
  ggplot(aes(x = views)) +
  geom_histogram() +
  labs(x = "Number of Views",
       y = "Count of Job Listings",
       title = " Fig. 1 Distribution of the 
       Number of Views 
       of a Job Listing") 
app_dist <- linkedin |>
  ggplot(aes(x = applies)) +
  geom_histogram() +
  labs(x = "Number of Applications Recieved",
       y = "Count of Job Listings",
       title = "Fig 2. Distribution of the 
       Number of Applications 
       Recieved") 
views_dist + app_dist
```

```{r applies_summary}
#| echo: false
summary(linkedin$applies)
```

Fig 1. The distribution of the number of applications for a job listing on LinkedIn is right-skewed and uni-modal, with fewer applications for a job listing most prevalent. Given that the distribution is skewed, the center is 8 applications, as estimated by the median. The IQR describing the spread of the middle 50% of data is 23 applications (26 - 3). There are 2 major outliers. One popular position is the job listing for Customer Success Manager at Noom with 1420 applications, another is the Customer Service Representative at Position Purpose with 980 applications.

```{r views_summary}
summary(linkedin$views)
```

Fig 2. The distribution of the number of views for a job listing on LinkedIn is right-skewed and uni-modal, with fewer views for a job listing most prevalent. Given that the distribution is skewed, the center is 54 views, as estimated by the median. The IQR describing the spread of the middle 50% of data is 103 views (126-23). There is one major outlier with more than 5000 views: the job listing for Customer Success Manager at Noom.

```{r views_dist_relationship}
#| echo: false
#| fig_width: 5 
#| fig_height: 1
views_apps <- linkedin |>
  ggplot(aes(x = applies, y = views)) +
  geom_point() +
  geom_smooth(method = 'lm',formula = y ~ x, se = F) +
  labs(x = "Number of Views",
       y = "Number of Applications",
       title = "Fig. 3 Number of Applications
       by Number of Views") 
worktype <- linkedin |> 
  ggplot(aes(x = as.factor(formatted_work_type))) + 
  geom_bar() + 
  labs(x = "Work Format Type",
       y = "Number of Positions",
       title = "Fig 4. Distribution of the 
      Work Type Format") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
views_apps + worktype 
```

Fig 3. We suspected that the number of applications is heavily influenced by the number of views the application gets. The relationship between the number of views and the number of applications is positive and linear, meaning as the number of views increases, so does the number of applications for a job listing on LinkedIn, on average. The bulk of the data is clustered in the range of 1-250 views and 1-1000 applications, with some exceptions. There are a handful of listings with number of views and applications far above the majority of the data, especially the listings at Noom and Position Purpose.

Fig 4. The levels of `formatted_work_type` include contract, full-time, internship, other, part-time, temporary, and volunteer. This histogram describing the distribution of work format type illustrates that a majority of the positions listed are full-time position, with over 7000 positions. Contract is the second most common work format type with slightly over 1500 positions. The other positions, including internship, other, part-time, temporary, and volunteer, have very few positions relative to full-time positions.

```{r work_type_relationship}
#| echo: false
#| fig_width: 5 
#| fig_height: 1
worktype_apps <- linkedin |>
  ggplot(aes(x = annual_max_salary, y = applies, color = formatted_work_type)) +
  geom_point() +
  geom_smooth(method = 'lm',formula = y ~ x, se = F) +
  labs(color = "Type of Work",
       x = "Max Annual Salary (Thousands of USD)",
       y = "Number of Applications",
       title = "Number of Applications by Maximum Annual Salary in 
       Thousands of USD and Type of Work")
worktype_apps
```

There could be an interaction effect between the type of work format of the job and the maximum annual salary, as a temporary or part-time position has less time to contribute and therefore recieve less. There overall appears to be a weak effect on the number of applications, but there appears to be a larger effect of type of work on temporary positions.

```{r}
#| echo: false
linkedin2 <- linkedin |> 
  drop_na(formatted_experience_level) |>
  filter(formatted_experience_level != "")
```

```{r}
#| echo: false
#| fig_width: 5 
#| fig_height: 1
experience_apps <- linkedin2 |>
  ggplot(aes(x = views, y = applies, color = formatted_experience_level)) +
  geom_point() + 
  geom_smooth(method = 'lm',formula = y ~ x, se = F) +
  labs(x = "Number of Views",
       y = "Number of Applications",
       color = "Experience Level",
       title = "Number of Applications Based on the 
       Experience Level Required and Views")
experience_apps
```
