---
title: "Your project title"
author: "Team Name: Team member 1, Team member 2, Team member 3, Team member 4"
date: "Update date"
format: pdf
execute: 
  warning: false
  message: false
  echo: false
editor: visual
---

```{r}
#| label: load packages and data

```

Your written report goes here!

::: callout-important
Before you submit, make sure your code chunks are turned off with `echo: false` and there are no warnings or messages with `warning: false` and `message: false` in the YAML.
:::

￼


```{r}
#| label: load packages and data
library(tidyverse)
library(tidymodels)
library(knitr)
library(patchwork)
job_postings <-read.csv("data/job_postings.csv")
benefits <-read.csv("data/benefits.csv")
employee <-read.csv("data/employee_counts.csv")
```

Your written report goes here!

::: callout-important
Before you submit, make sure your code chunks are turned off with `echo: false` and there are no warnings or messages with `warning: false` and `message: false` in the YAML.
:::


```{r manipulating_benefits}
#| echo: false
benefits <- benefits |>
  select(-inferred) |>
  mutate(count = 1) |>
  pivot_wider(names_from = "type", values_from = "count")
```


```{r joining_jobs_employee}
#| echo: false
jobs_employee <- job_postings |>
  left_join(employee, by = join_by("company_id"))
```

```{r joining_final_set}
#| echo: false
linkedin <- jobs_employee |>
  left_join(benefits, by = join_by("job_id"))

linkedin <- linkedin |> distinct(job_id, .keep_all = TRUE)
```


```{r}
linkedin <- linkedin |>
  mutate(per_applies = applies/views) |>
  filter(per_applies < 1)
```

```{r mutate_pay_nums}
#| warning: false
#| echo: false
linkedin <- linkedin |>
  mutate(pay_period = recode(pay_period, YEARLY = 1, HOURLY = 2080))
```

```{r annual_salary_manipulation}
#| echo: false
linkedin <- linkedin |>
   mutate(annual_max_salary = pay_period * max_salary/1000)
```

```{r}
linkedin |>
  filter(annual_max_salary > 500)
```


```{r}
names(linkedin)
```
```{r}
linkedin
```


```{r}
linkedin |>
  ggplot(aes(x = annual_max_salary, y = per_applies)) +
  geom_point()
```

```{r}
linkedin |>
  ggplot(aes(x = per_applies)) + 
  geom_histogram()
```



```{r}
linkedin
```


```{r}
set.seed(210)

linkedin_split <- initial_split(linkedin)
linkedin_train <- training(linkedin_split)
linkedin_test  <- testing(linkedin_split)
```




```{r}
linkedin_fit <- linear_reg() |>
  set_engine("lm") |>
#  fit(per_applies ~ med_salary + formatted_work_type + formatted_experience_level, data = linkedin_train)
  fit(per_applies ~ med_salary, data = linkedin_train)


tidy(linkedin_fit) |> 
  kable(digits = 2)

```

```{r}
glance(linkedin_fit)
```






