---
title: "Your project title"
author: "Team Name: Team member 1, Team member 2, Team member 3, Team member 4"
date: "Update date"
format: pdf
execute: 
  warning: false
  message: false
  echo: false
editor: visual
---

```{r}
#| label: load packages and data

```

Your written report goes here!

::: callout-important
Before you submit, make sure your code chunks are turned off with `echo: false` and there are no warnings or messages with `warning: false` and `message: false` in the YAML.
:::

￼


```{r}
#| label: load packages and data
library(tidyverse)
library(tidymodels)
library(knitr)
library(patchwork)
job_postings <-read.csv("data/job_postings.csv")
benefits <-read.csv("data/benefits.csv")
employee <-read.csv("data/employee_counts.csv")
```

Your written report goes here!

::: callout-important
Before you submit, make sure your code chunks are turned off with `echo: false` and there are no warnings or messages with `warning: false` and `message: false` in the YAML.
:::


```{r manipulating_benefits}
#| echo: false
benefits <- benefits |>
  select(-inferred) |>
  mutate(count = 1) |>
  pivot_wider(names_from = "type", values_from = "count")
```

```{r}

benefits <- replace(benefits, is.na(benefits), 0)
benefits$tot_benefits <- rowSums(benefits == 1)
benefits_total <- benefits[, c('job_id', 'tot_benefits')]
```



```{r joining_jobs_employee}
#| echo: false
jobs_employee <- job_postings |>
  left_join(employee, by = join_by("company_id"))
```

```{r joining_final_set}
#| echo: false
linkedin <- jobs_employee |>
  left_join(benefits_total, by = join_by("job_id"))

linkedin_yearly <- linkedin |> 
  distinct(job_id, .keep_all = TRUE) |>
  mutate(per_applies = applies/views) |>
  filter(per_applies < 1) |>
  filter(pay_period == "YEARLY") |>
  mutate(original_listed_time = as.POSIXct(original_listed_time/1000, origin = "1970-01-01", tz = "EST")) 

linkedin_yearly$hour <- sapply(strsplit(as.character(linkedin_yearly$original_listed_time), ' '), function(x) {
  time_parts <- unlist(strsplit(x[2], ':'))
  return(time_parts[1])
})
```

```{r}
linkedin_yearly
```

```{r}
linkedin_yearly |>
  ggplot(aes(x = hour, y = per_applies)) + 
  geom_point()
```



```{r}
# Sample data frame
data <- data.frame(timestamp = c('2023-11-12 08:30:45', '2023-11-12 15:45:20', '2023-11-12 22:10:05'))

# Splitting timestamp and extracting the hour
data$hour <- sapply(strsplit(as.character(data$timestamp), ' '), function(x) {
  time_parts <- unlist(strsplit(x[2], ':'))
  return(time_parts[1])
})

# Display the resulting data frame
print(data)

```


```{r}
linkedin_yearly
```

```{r}
#1692732000000
timestamp <- 1692732000

#timestamp <- 1692817626
formatted_date <- as.POSIXct(timestamp, origin = "1970-01-01", tz = "UTC")
print(formatted_date)

```



```{r}
linkedin_yearly |>
  filter(employee_count < 1000) |>
  ggplot(aes(x = employee_count, y = per_applies)) + 
  geom_point()
```


```{r}
linkedin_hourly <- linkedin |> 
  distinct(job_id, .keep_all = TRUE) |>
  mutate(per_applies = applies/views) |>
  filter(per_applies < 1) |>
  filter(pay_period == "YEARLY")
```


```{r}
set.seed(210)
linkedin_split <- initial_split(linkedin_yearly, prop = 0.8)
linkedin_train <- training(linkedin_split)
linkedin_test <- testing(linkedin_split)
```

```{r}
linkedin_train
```


```{r}

linkedin_yr_rec <- recipe(per_applies ~ job_id + max_salary + follower_count + formatted_experience_level, data = linkedin_train) |> 
  update_role(job_id, new_role = "ID") |> 
  step_mutate(max_salary = max_salary / 1000000) |>
  step_mutate(follower_count = follower_count / 100000000) |>
  step_naomit(all_predictors()) |>
  step_dummy(all_nominal_predictors()) |> 
  step_zv(all_predictors())
```

```{r}
linkedin_yr_rec1 <- recipe(per_applies ~ job_id + max_salary + follower_count, data = linkedin_train) |> 
  update_role(job_id, new_role = "ID") |> 
  step_mutate(max_salary = max_salary / 1000000) |>
  step_mutate(follower_count = follower_count / 100000000) |>
  step_naomit(all_predictors()) |>
  step_dummy(all_nominal_predictors()) |> 
  step_zv(all_predictors())
```

```{r}

linkedin_yr_rec_ben <- recipe(per_applies ~ job_id + max_salary + tot_benefits, data = linkedin_train) |> 
  update_role(job_id, new_role = "ID") |> 
  step_mutate(max_salary = max_salary / 1000000) |>
  #step_mutate(follower_count = follower_count / 100000000) |>
  step_naomit(all_predictors()) |>
  step_dummy(all_nominal_predictors()) |> 
  step_zv(all_predictors())
```

```{r}
linkedin_yr_rec_hr <- recipe(per_applies ~ job_id + max_salary + hour, data = linkedin_train) |> 
  update_role(job_id, new_role = "ID") |> 
  step_mutate(max_salary = max_salary / 1000000) |>
  step_naomit(all_predictors()) |>
  step_dummy(all_nominal_predictors()) |> 
  step_zv(all_predictors())
```




```{r}
#specify the model
linkedin_yr_spec <- linear_reg() |>
  set_engine("lm")

#build model workflow
linkedin_yr_workflow <- workflow() |>
  add_model(linkedin_yr_spec) |>
  add_recipe(linkedin_yr_rec) 

# fit the model 
linkedin_yr_fit <- linkedin_yr_workflow |>
  fit(data = linkedin_train) 

tidy(linkedin_yr_fit) |>
  kable(digits = 3)
```

```{r}
#specify the model
linkedin_yr_spec1 <- linear_reg() |>
  set_engine("lm")

#build model workflow
linkedin_yr_workflow1 <- workflow() |>
  add_model(linkedin_yr_spec1) |>
  add_recipe(linkedin_yr_rec1) 

# fit the model 
linkedin_yr_fit1 <- linkedin_yr_workflow1 |>
  fit(data = linkedin_train) 

tidy(linkedin_yr_fit1) |>
  kable(digits = 3)
```

```{r}
#specify the model
linkedin_yr_spec_ben <- linear_reg() |>
  set_engine("lm")

#build model workflow
linkedin_yr_workflow_ben <- workflow() |>
  add_model(linkedin_yr_spec_ben) |>
  add_recipe(linkedin_yr_rec_ben) 

# fit the model 
linkedin_yr_fit_ben <- linkedin_yr_workflow_ben |>
  fit(data = linkedin_train) 

tidy(linkedin_yr_fit_ben) |>
  kable(digits = 3)
```
```{r}
#specify the model
linkedin_yr_spec_hr <- linear_reg() |>
  set_engine("lm")

#build model workflow
linkedin_yr_workflow_hr <- workflow() |>
  add_model(linkedin_yr_spec_hr) |>
  add_recipe(linkedin_yr_rec_hr) 

# fit the model 
linkedin_yr_fit_hr <- linkedin_yr_workflow_hr |>
  fit(data = linkedin_train) 

tidy(linkedin_yr_fit_hr) |>
  kable(digits = 3)
```


BIC-- -2771, -2757, -1315
```{r}
glance(linkedin_yr_fit1)
```

```{r}
glance(linkedin_yr_fit)
```
```{r}
glance(linkedin_yr_fit_ben)
```

```{r}
glance(linkedin_yr_fit_hr)
```

```{r}
linkedin_yr_fit_5 <- linear_reg() |>
  fit(per_applies~ hour + max_salary, data = linkedin_train) 

glance(linkedin_yr_fit_5)
```

```{r}
linkedin_yr_fit_5 <- linear_reg() |>
  fit(per_applies~ sponsored, data = linkedin_train) 

glance(linkedin_yr_fit_5)
```


```{r}
linkedin_new <- linkedin_yearly |>
  mutate(applied_10 = if_else(per_applies > 0.1, 1, 0))
```


```{r}
linkedin_new <- linkedin_yearly |>
  mutate(applied_10 = if_else(per_applies > 0.1, 1, 0))
linkedin_new$applied_10 <- as.factor(linkedin_new$applied_10)
linkedin_new
```

```{r}
linkedin_new <- linkedin_yearly |>
  mutate(applied_10 = if_else(per_applies > 0.1, 1, 0))
linkedin_new$applied_10 <- as.factor(linkedin_new$applied_10)

set.seed(210)

linkedin_split_new <- initial_split(linkedin_new)
linkedin_train_new <- training(linkedin_split_new)
linkedin_test_new  <- testing(linkedin_split_new)


linkedin_yr_fit_log <- logistic_reg() |>
  set_engine("glm") |>
  fit(applied_10~ max_salary, data = linkedin_train_new, family = "binomial") 

glance(linkedin_yr_fit_log)
```

```{r}
linkedin_pred <- predict(linkedin_yr_fit_log, linkedin_test_new, type = "prob") |> 
  bind_cols(linkedin_test_new) 

linkedin_pred |>
  roc_curve(
    truth = applied_10,
    .pred_1,
    event_level = "second"
  ) |>
  autoplot()
```



```{r}
linkedin_new
```


```{r}
linkedin_new |>
  ggplot(aes(x = tot_benefits, y = per_applies)) + 
  geom_point()
```

```{r}
linkedin_new
```
